Scheeper's Meager-NWD Game and the Menger Game

### 2014-08-25 phd/dissertation/_raw_chapter3.tex
Finish ch 2 draft, outline of results for ch 3, ch 6
Name and camelCase based game commands/definitions

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

@@

\begin{defn} 
Gruenhage's open-point convergence game $\congame{X}{x}$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{defn}

@@

\begin{prop}
$O\codewin \congame{\oneptcomp{\kappa}}{\infty}$ for all cardinals $\kappa$.
\end{prop}

@@

\begin{prop}
$O\prewin \congame{\oneptcomp{\omega}}{\infty}$.
\end{prop}

@@

\begin{prop}
$O\not\prewin \clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
\end{prop}

@@

\begin{prop}
$O\tactwin\congame{\oneptcomp{\omega}}{\infty}$.
\end{prop}

@@

\begin{thm}
$O\not\ktactwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
\end{thm}

@@

\begin{thm}
$O\markwin \clusgame{\oneptcomp{\omega_1}}{\infty}$.
\end{thm}

@@

\begin{prop}
$O\uparrow\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{prop}

@@

\begin{thm}
For all cardinals $\kappa\leq 2^\omega$, $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{thm}

@@

\begin{thm}
Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$. (That is, $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.) Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{thm}

@@

\begin{thm}
Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$. Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{thm}

@@

We turn our attention to $\congame{\sigmaprodr{\kappa}}{\vec{0}}$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) =\Sigma\mathbb{R}^\kappa \cap \prod_{\alpha<\kappa} U_\alpha$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.

@@

\begin{thm}
$F\codewin\pfgame{\kappa}$ for all cardinals $\kappa$.
\end{thm}

\begin{proof}
Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $F\codewin\pfgame{\kappa_n}$ using the strategy $\sigma_n(N,W)$ such that for $M\subseteq N$, $\sigma_n(M,W)\subseteq\sigma_n(N,W)$. Define \[\sigma(N,W)=(|N|+1)\cup\bigcup_{n<|N|}\sigma_n(N\cap\kappa_n,W\cap\kappa_n)\]

@@

Now suppose $F\codewin\pfgame{\kappa}$. For each $\alpha<\kappa^+$, let $\sigma_\alpha(N,W)$ be a winning coding strategy for $\pfgame{\alpha}$ such that for $M\subseteq N$, $\sigma_\alpha(M,W)\subseteq\sigma_\alpha(N,W)$. We define the following strategy for $F$ in $\pfgame{\kappa^+}$: \[\sigma(N,W)=N\cup\bigcup_{\alpha\in N}\sigma_{\alpha+1}(N\cap(\alpha+1),W\cap(\alpha+1))\]

@@

\begin{cor}
$O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$ for all cardinals $\kappa$.
\end{cor}

\begin{proof}
Let $\tau(N,W)$ be the winning coding strategy for $F$ in $\pfgame{\kappa}$, $N(U)\in[\kappa]^{<\omega}$ represent the non-$\mathbb{R}$ coordinates of a basic open set $U$ of $\sigmaprodr{\kappa}$, and $W(p)\in[\kappa]^{\leq\omega}$ represent the non-$0$ coordinates of a point $p$ in $\sigmaprodr{\kappa}$. For each $\alpha<\kappa$, let \[\sigma_\alpha(U,p)=\left\{\begin{array}{ll}(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})&\text{if }\alpha\in\tau(N(U),W(p))\\\mathbb{R}&\text{otherwise}\end{array}\right.\] and $\sigma(U,p)=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}\sigma_\alpha(U,p)$.
\end{proof}

>>>>

@@

\begin{defn}
Gruenhage's open-point convergence game $\gruConGame{X}{x}$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{defn}

@@

\begin{prop}
$O\codewin \gruConGame{\oneptcomp{\kappa}}{\infty}$ for all cardinals $\kappa$.
\end{prop}

@@

\begin{prop}
$O\prewin \gruConGame{\oneptcomp{\omega}}{\infty}$.
\end{prop}

@@

\begin{prop}
$O\not\prewin \gruClusGame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
\end{prop}

@@

\begin{prop}
$O\tactwin\gruConGame{\oneptcomp{\omega}}{\infty}$.
\end{prop}

@@

\begin{thm}
$O\not\ktactwin{k}\gruClusGame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
\end{thm}

@@

\begin{thm}
$O\markwin \gruClusGame{\oneptcomp{\omega_1}}{\infty}$.
\end{thm}

@@

\begin{prop}
$O\uparrow\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{prop}

@@

\begin{thm}
For all cardinals $\kappa\leq 2^\omega$, $O\codewin\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{thm}

@@

\begin{thm}
Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$. (That is, $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.) Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{thm}

@@

\begin{thm}
Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$. Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{thm}

@@

We turn our attention to $\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) =\Sigma\mathbb{R}^\kappa \cap \prod_{\alpha<\kappa} U_\alpha$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.

@@

\begin{thm}
$F\codewin\cloPFGame{\kappa}$ for all cardinals $\kappa$.
\end{thm}

\begin{proof}
Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $F\codewin\cloPFGame{\kappa_n}$ using the strategy $\sigma_n(N,W)$ such that for $M\subseteq N$, $\sigma_n(M,W)\subseteq\sigma_n(N,W)$. Define \[\sigma(N,W)=(|N|+1)\cup\bigcup_{n<|N|}\sigma_n(N\cap\kappa_n,W\cap\kappa_n)\]

@@

Now suppose $F\codewin\cloPFGame{\kappa}$. For each $\alpha<\kappa^+$, let $\sigma_\alpha(N,W)$ be a winning coding strategy for $\cloPFGame{\alpha}$ such that for $M\subseteq N$, $\sigma_\alpha(M,W)\subseteq\sigma_\alpha(N,W)$. We define the following strategy for $F$ in $\cloPFGame{\kappa^+}$: \[\sigma(N,W)=N\cup\bigcup_{\alpha\in N}\sigma_{\alpha+1}(N\cap(\alpha+1),W\cap(\alpha+1))\]

@@

\begin{cor}
$O\codewin\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$ for all cardinals $\kappa$.
\end{cor}

\begin{proof}
Let $\tau(N,W)$ be the winning coding strategy for $F$ in $\cloPFGame{\kappa}$, $N(U)\in[\kappa]^{<\omega}$ represent the non-$\mathbb{R}$ coordinates of a basic open set $U$ of $\sigmaprodr{\kappa}$, and $W(p)\in[\kappa]^{\leq\omega}$ represent the non-$0$ coordinates of a point $p$ in $\sigmaprodr{\kappa}$. For each $\alpha<\kappa$, let \[\sigma_\alpha(U,p)=\left\{\begin{array}{ll}(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})&\text{if }\alpha\in\tau(N(U),W(p))\\\mathbb{R}&\text{otherwise}\end{array}\right.\] and $\sigma(U,p)=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}\sigma_\alpha(U,p)$.
\end{proof}
